%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Project Applicant and Developer Intern} % Job title
    {iFLYTEK Co., Ltd.} % Organization
    {Wuhan, China} % Location
    {Jul. 2021 - Sep. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for project declaration, development, docking, acceptance, and launch, etc.}
        \item {Conducted research on the development of digital economy industry and optical fiber interception.}
        \item {Using librosa, WebrtcVAD, Pytorch and UIS-RNN classification algorithms under Python, the speech extraction under the TIMIT corpus was completed, including basic speech noise reduction, framing, separation, classification, recognition, etc.}
        \item {Speech extraction accuracy: 98\%, Speech recognition accuracy: 97\% (Test set: Texas Instruments, MIT, SRI International TIMIT continuous speech corpus)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Assistant at Visa Service Center of the Ministry of Europe} % Job title
    {Hubei Provincial Foreign Affairs Office} % Organization
    {Wuhan, China} % Location
    {Jun. 2019 - Sep. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Coordinated and arranged more than 10 colleagues to receive scholars from Babis-Bojay University in Romania for a week-long friendly exchange activity in Hubei Province}
        \item {Completed bilingual translation of 6 relevant work documents and reports in both Chinese and English}
        \item {Use Excel and PPT to participate in planning and organize the itinerary during the Han Dynasty. List the optional information of 30+ attractions and projects, and select the best plan according to factors such as time, personnel and weather, which is adopted by leaders}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
